An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-30 uai2017/paper.tex
Fixed table caption to say 10 trials. NOW let's re-submit to UAI.
Adding UAI arxiv version and UAI paper submission (without names)

% Daniel Seita: upon submission, comment out all authors, un-comment the
% following two lines:
\author{} % LEAVE BLANK FOR ORIGINAL SUBMISSION.
          % UAI  reviewing is double-blind.

% The author names and affiliations should appear only in the accepted paper.
%% \author{
%% Daniel Seita$^1$, 
%% Xinlei Pan$^1$,
%% Haoyu Chen$^1$,
%% John Canny$^{1,2}$ \\
%% $^1$ University of California, Berkeley, CA \\
%% $^2$ Google Research, Mountain View, CA\\ 
%% \texttt{\{seita,xinleipan,haoyuchen,canny\}@berkeley.edu}
%% }

@@

\begin{table}[t]
\caption{Gaussian Mixture Model Statistics}
\small
\label{tab:poissons}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Metric/Method} & {\sc MHminibatch} & {\sc AustereMH(c)} & {\sc MHSubLhd} \\
\hline
\T Equation~\ref{eq:log_prob_poissons} & $-1307.0 \pm 229.5$ & $-1386.9 \pm 322.4$ & $-1295.1 \pm 278.0$ \\
Chi-Squared & $4502.3 \pm 1821.8$ & $ 5216.9 \pm 3315.8$ & $ 3462.3 \pm 1519.5$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

>>>>

% Daniel Seita: upon submission, comment out all authors, un-comment the
% following two lines:
%\author{} % LEAVE BLANK FOR ORIGINAL SUBMISSION.
%          % UAI  reviewing is double-blind.

% The author names and affiliations should appear only in the accepted paper.
\author{
Daniel Seita$^1$, 
Xinlei Pan$^1$,
Haoyu Chen$^1$,
John Canny$^{1,2}$ \\
$^1$ University of California, Berkeley, CA \\
$^2$ Google Research, Mountain View, CA\\ 
\texttt{\{seita,xinleipan,haoyuchen,canny\}@berkeley.edu}
}

@@

\begin{table}[t]
\caption{Gaussian Mixture Model statistics ($\pm$ one standard deviation over 10
trials).}
\small
\label{tab:poissons}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Metric/Method} & {\sc MHminibatch} & {\sc AustereMH(c)} & {\sc MHSubLhd} \\
\hline
\T Equation~\ref{eq:log_prob_poissons} & $-1307.0 \pm 229.5$ & $-1386.9 \pm 322.4$ & $-1295.1 \pm 278.0$ \\
Chi-Squared & $4502.3 \pm 1821.8$ & $ 5216.9 \pm 3315.8$ & $ 3462.3 \pm 1519.5$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}
